%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListStartt}{
  \begin{itemize}[leftmargin=*, itemsep=4pt, parsep=0pt, topsep=2pt]
}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubHeadingListEndd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeBullet}[1]{
  \item \small{#1 \vspace{-2pt}}
}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/basant-kumar-462b55186/}{\Large Basant Kumar}} & Email : \href{https://www.linkedin.com/in/basant-kumar-462b55186/}{basantsaini17220545@gmail.com}\\
  \href{https://www.linkedin.com/in/basant-kumar-462b55186/}{linkedin.com/in/basant-kumar-462b55186} & Mobile : 9027385476\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology(IIT)}{DHANBAD}
      {B.Tech - Computer Science And Engineering}{Jul. 2018 -- May. 2022}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStartt
   \item{
     \textbf{Languages \& Frameworks}{: Java, Spring, Spring Boot} 
   }
   \item{ 
     \textbf{Databases}{: MySQL, Postgres, MongoDB}
   }
      \item{
     \textbf{Cloud \& DevOps}{: Docker, Kubernetes, Azure, Jenkins, Git}
   }
    \item{
     \textbf{Messaging \& Observability: }{: Kafka, OpenTelemetry, Prometheus & Grafana}
   }
   \item{
     \textbf{Build \& Quality}{: Maven, Gradle, Sonar}
   }
    \item{
     \textbf{Data/Integration:}{: Apache NiFi}
   }
      \item{
     \textbf{Caching}{: Redis}
     
   }
 \resumeSubHeadingListEndd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AJIO}{Banglore}
      {Software Engineer II}{Jul 2023 - Present}
      \resumeItemListStart
        \resumeBullet
          {Led the migration from a Hybris monolith to a distributed microservices architecture— owning end-to-end solutioning, system design, and implementation.}
        \resumeBullet
          {Architected and built the Order Gateway Service, orchestrating forward order, exchange, return, and cancellation flows with high availability and scalability.}
        \resumeBullet
          {Designed and delivered an Address Book Service for managing customer delivery addresses with geo-location and pincode-based lookup capabilities.}
        \resumeBullet
          {Developed a Selfcare Service (CRM) enabling streamlined complaint resolution, FAQ management, and customer query handling.}
        \resumeBullet
          {Built the NPS Service to capture customer feedback, conduct surveys, and record RTO reason data — driving actionable insights for post-purchase experience improvement.}
        \resumeBullet
          {Owned the Unified Authentication & Authorization Service (UAAS), implementing secure customer-facing and service-to-service authentication across the platform.}
       \resumeItemListEnd

    \resumeSubheading
      {AJIO}{Banglore}
      {Software Engineer}{Jun 2022 - Jun 2023}
      \resumeItemListStart
        \resumeBullet
            {Built the AJIO CMS tool from the ground up, delivering a scalable, high-performance content management platform powering the AJIO storefront.}
        \resumeBullet
            {Improved CMS scalability, resilience, and deployment velocity by integrating Redis-based caching, Docker containerization, and Kubernetes orchestration.}
        \resumeBullet
            {Contributed to AJIO Gram, a social engagement platform supporting posts and stories.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Sign Language Detector}
      {Built an ML model to translate sign language into English. Used TensorFlow, Keras, NumPy, OpenCV, and Python; trained and validated in Jupyter. Focused on real‑time gesture recognition and accurate text output.}
    \resumeSubItem{Nearby Shopping App (Android)}
      {Developed an Android app for categorized shopping and direct store communication. Integrated Firebase, Firebase ML Kit, and Google Maps API. Enabled nearby store discovery with real‑time store timing updates.}
  \resumeSubHeadingListEnd

%
%-------------------------------------------
\end{document}
